Mitigating Interest Flooding DDoS Attacks in NDN

### 2013-01-11 eval-large-scale.tex
Another variant of discussion section, acknowledging potential problems and handwaving that the problem is not that serious.
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@875 df1a90cd-247b-4364-bdaf-287a704eb499
Updates and renaming
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@895 df1a90cd-247b-4364-bdaf-287a704eb499

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.26,angle=90]{7018-r0}
  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
  \label{fig:large-scale-topo}
\end{figure}

@@

The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that for both physical limits algorithms and dynamic limits algorithm the performance is about the same as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.

\begin{figure}[tbh]
 \centering
 \includegraphics[scale=1]{topo-7018-gw-15mins-new/7018-r0-good-0-producer-gw}
 \caption{Satisfaction ratio dynamics during the attack (30\% attackers)}
 % producer on a gateway node
 \label{fig:large-scale}
\end{figure}

At the same time, the probabilistic method completely failed to provide an adequate protection against the Interest flooding attack, and in addition degraded service for the legitimate users after the attack finished.
The main reason for the failure was already explained in Section~\ref{sec:probabilistic}.
That is, if the number of hops between legitimate users and the Data producer is large (15 on average in the simulated topology) uncoordinated probabilistic Interest drops result in minuscule probability for good Interests to reach the Data producer during an ongoing attack, resulting in negative Interests satisfaction ratio statistics.
This also explains why until the statistics ages out, not all legitimate users can get satisfy all of their Interests.

In summary, in all of the simulated topologies, the dynamic limits algorithm largely restricts malicious traffic to even enter the network.
The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.

>>>>

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.15,angle=90]{7018-r0}
  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}
  \label{fig:large-scale-topo}
\end{figure}

@@

The evaluation results,\footnote{Note that for larger-scale experiments we reduced attack window to 15~minutes} summarized in Fig.~\ref{fig:large-scale}, show that performance of the token bucket with per interface fairness and satisfaction-based pushback algorithms are about at the same level as in small-scale evaluations (Fig.~\ref{fig:small-scale}), but with larger variations of minimum and maximum instantaneous satisfaction rates.

\begin{figure}[tbh]
 \centering
 \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
 \caption{Satisfaction ratio dynamics during the attack (30\% attackers)}
 % producer on a gateway node
 \label{fig:large-scale}
\end{figure}

At the same time, the satisfaction-based Interest acceptance method completely failed to provide an adequate protection against the Interest flooding attack, and in addition degraded service for the legitimate users after the attack finished.
The main reason for the failure was already explained in Section~\ref{sec:probabilistic}.
That is, if the number of hops between legitimate users and the Data producer is large (15 on average in the simulated topology) uncoordinated probabilistic Interest drops result in minuscule probability for good Interests to reach the Data producer during an ongoing attack, resulting in negative Interests satisfaction ratio statistics.
This also explains why until the statistics ages out, not all legitimate users can get satisfy all of their Interests.

In summary, in all of the simulated topologies, the satisfaction-based pushback algorithm restricts malicious traffic from even entering the network.
The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack).
As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.

### 2013-01-11 eval-small-scale.tex
Updates and renaming
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@895 df1a90cd-247b-4364-bdaf-287a704eb499

The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either physical limits, physical limits with per-interface fairness, probabilistic Interest accept, or dynamic limits (Section~\ref{sec:design}).

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw}
  \caption{Satisfaction ratio dynamics during the attack (7 attackers / 9 legitimate)}
  \label{fig:small-scale attack progress}
\end{figure}

\paragraph{\textbf{Physical limits}}

@@

\paragraph{\textbf{Physical limits with per-interface fair queueing}}

@@

\paragraph{\textbf{Probabilistic Interest accept}}

When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
The observed periodicity of the probabilistic Interest accept curve on Fig.~\ref{fig:small-scale attack progress} is a direct result from ``intelligence'' (Interest satisfaction rate statistics) decaying with time.
The 50-second periods approximately correspond to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx20\%$ within 50~seconds.
The primary reason that such minimum peaks exist is the fact that when attack Interests start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe traffic mix from legitimate and malicious users).
This degradation subsequently reduces chances for legitimate Interests get through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' to the edge.

\paragraph{\textbf{Dynamic limits}}

The only potential problem with the dynamic limits algorithm is that it features a sharp dive of the satisfaction ratio curve at the start of the attack.
That is, until all routers become fully aware of the attack---malicious Interests start to time out---and until explicit Interest limits announcements successfully localize malicious Interests near the attacker, the network for a short period of time (under 10~seconds for all simulation runs) fails to provide 100\% service for the legitimate users.
At the same time, we do not observe any periodic behavior, as dynamically adjusted limits during an ongoing attack effectively guarantee that once Interest is admitted, it will get through to the Data producer.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.9]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-avg-1-min}
  \caption{Average consumer Interest satisfaction ratios (first minute)}
  \label{fig:small-scale-topo boxplot}
\end{figure}

The presented results demonstrate the overall, and somewhat obvious, trends for all attack mitigation algorithms: the larger is the attack, the lower service quality is observed by the legitimate users.
Physical limits with and without per-interface fairness give perfect attack instrument even for a small number of attackers: just 3 attackers can either completely shut down or halve the service quality for the rest 13 users.
At the same time, while both intelligent attack mitigation algorithms also show a decline in service quality, this decline is very subtle: when more than 50\% of users are compromised, service degrades less than by 25\% for probabilistic Interest accept method and less than by 10\% in dynamic limits algorithm.

>>>>

The first set of experiments aims to evaluate reaction of the network and Interest flooding attack mitigation methods mechanisms under a moderate-level DDoS attack.
For this purpose, we simulated four different network scenarios, in which all routers implements the same attack mitigation algorithm, either token bucket with per interface fairness, satisfaction-based Interest acceptance, or satisfaction-based pushback (Section~\ref{sec:design}).

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
  \caption{Satisfaction ratio dynamics during the attack (7 attackers / 9 legitimate)}
  \label{fig:small-scale attack progress}
\end{figure}

\paragraph{\textbf{Simple token buckets}}

{\color{red}Alex: should this discussion be removed or we still want to keep it (as it is referenced later and potentially before)}

@@

\paragraph{\textbf{Token bucket with per interface fairness}}

@@

\paragraph{\textbf{Satisfaction-based Interest acceptance}}

When routers more intelligently process incoming Interests (i.e., based on the incoming interface statistics), the Interest flooding attack becomes virtually ineffective.
That is, malicious Interests are simply not getting admitted to the network, not being able to create much service disturbance for the legitimate users.
The observed periodicity of the satisfaction-based Interest accept curve on Fig.~\ref{fig:small-scale attack progress} is a direct result from ``intelligence'' (Interest satisfaction rate statistics) decaying with time.
The 50-second periods approximately correspond to the selected exponential decaying parameter $\alpha=e^{−1.0/30.0}$, which decays statistics to $1/e$ of the initial value within 30~seconds and to $\approx20\%$ within 50~seconds.
The primary reason that such minimum peaks exist is the fact that when attack Interests start to get readmitted, they cause degradation of statistics on routers close to the producer (i.e., routers that observe traffic mix from legitimate and malicious users).
This degradation subsequently reduces chances for legitimate Interests get through (see Section~\ref{sec:probabilistic}) until malicious Interests are ``pushed back'' to the edge.

\paragraph{\textbf{Satisfaction-based pushback}}

The only potential problem with the satisfaction-based pushback algorithm is that it features a sharp dive of the satisfaction ratio curve at the start of the attack.
That is, until all routers become fully aware of the attack---malicious Interests start to time out---and until explicit Interest limits announcements successfully localize malicious Interests near the attacker, the network for a short period of time (under 10~seconds for all simulation runs) fails to provide 100\% service for the legitimate users.
At the same time, we do not observe any periodic behavior, as dynamically adjusted limits during an ongoing attack effectively guarantee that once Interest is admitted, it will get through to the Data producer.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
  \caption{Average consumer Interest satisfaction ratios (first minute)}
  \label{fig:small-scale-topo boxplot}
\end{figure}

The presented results demonstrate the overall, and somewhat obvious, trends for all attack mitigation algorithms: the larger is the attack, the lower service quality is observed by the legitimate users.
Physical limits with and without per-interface fairness give perfect attack instrument even for a small number of attackers: just 3 attackers can either completely shut down or halve the service quality for the rest 13 users.
At the same time, while both intelligent attack mitigation algorithms also show a decline in service quality, this decline is very subtle: when more than 50\% of users are compromised, service degrades less than by 25\% for the satisfaction-based Interest accept method and less than by 10\% in the satisfaction-based pushback algorithm.
